\cvsection{Profile}

\small I am a final-year Ph.D. Student at Warwick University.
My work has focused on the development of software tools to detect and characterise artificial debris in optical telescope images. \\
I am also passionate about outreach, and have been involved in numerous efforts to promote HE and STEM in local schools.

\medskip

\cvsection{Education}

\textbf{Ph.D.\ in Space Science} | Uni. Warwick, UK \\ \faCalendar \hspace{2pt} Sept 2017 -- Ongoing \\
\small Funding: Science \& Technology Facilities Council \\
Supervisor: Don Pollacco

\smallskip

\textbf{M.Phys.\ in Physics} | Uni. Warwick, UK \\ \faCalendar \hspace{2pt} Sept 2013 -- June 2017 \\
\small Grade: First Class Honours \\
Key topics: Mechanics, Relativity, Quantum, \\ Electricity \& Magnetism, Materials, Computing, Electronics, Astronomy 

\smallskip

\textbf{A Levels \& GCSEs} | Wrenn Sixth Form, UK \\ \faCalendar \hspace{2pt} Sept 2010 -- June 2013 \\
\small A2: Maths (A*), Hist. (A*), Phys. (A), Chem. (A) \\
AS: Above 4(A), Furth. Maths (A), Phil. (B) \\
GCSE: 9(A*) incl. Maths, IT, Eng. Lang. \& 5(A)

\medskip

%\cvsection{Awards}

%\faTrophy \hspace{2pt} \textbf{Best Student Paper} -- \href{https://amostech.com/2019-archive/}{Novel work} \\ 2019 | AMOSTECH, Maui, Hawai'i, US

%\smallskip

%\faTrophy \hspace{2pt} \textbf{Best Poster} -- \href{https://warwick.ac.uk/fac/cross_fac/iatl/news/posters-in-parliament-2018}{Posters in Parliament} \\ 2018 | Palace of Westminster, London, UK

%\smallskip

%\faTrophy \hspace{2pt} \textbf{Significant Contribution} -- Outreach \\ 2016 | SROAS Office, Uni. Warwick, UK

%\smallskip

%\faTrophy \hspace{2pt} \textbf{Best Examination Performance} -- GCSEs \\ 2011 | Wrenn School, UK

\cvsection{Computing}

\small \faGithub \hspace{2pt} \href{https://github.com/jblake95}{github/jblake95} for projects
\smallskip
\begin{itemize}
	\item \textbf{Operating systems} \\
	Linux, MacOS, Windows
	\item \textbf{Programming languages} \\
	Python, C, Bash
	\item \textbf{Selected libraries} \\
	NumPy, SciPy, Matplotlib, astropy, astroquery, SEP, datetime, rebound, Skyfield, ellc, emcee, pandas, json
	\item \textbf{Software packages} \\
	IRAF, SAOImage DS9, AstroImageJ, Astrometry.net, Origin Pro, MASTER, DRAMA
	\item \textbf{Developer tools} \\
	Git, PyCharm, Geany, Spyder
	\item \textbf{Word processing} \\
	\LaTeX, Microsoft Office, Libre Office
	\item \textbf{Common tasks} \\
	Data analysis, image reduction and processing, database querying, modelling, simulations
\end{itemize}

\medskip

\cvsection{References}

\normalsize \textbf{Available on request.}