\cvsection{Contact}

\begin{flushright}
\vspace{-1em}
\small Department of Physics\\
University of Warwick\\
Gibbet Hill Road\\
Coventry\\
CV4 7AL
\end{flushright}

\medskip

\cvsection{Research profile}
\vspace{-1em}
\small \justify I am a second-year postgraduate research student in the Astronomy Group at Warwick University.
My work is primarily focused on the detection and monitoring of artificial space debris. \\
I observe the night sky with optical telescopes and use this data to get accurate positions and brightnesses for satellites and debris. \\
Alongside this, I have a keen interest in the fields of exoplanets and astrobiology.

\medskip

\cvsection{Education}

\cvevent{Ph.D.\ in Space Science}{University of Warwick}{September 2017 -- Ongoing}{}
\vspace{-1em}
\small \justify \textbf{Supervisor:} Prof. Don Pollacco (Astronomy) \\
\textbf{Project:} \textit{The debris population at geostationary orbit and the fate of aged spacecraft} (see Experience)

\divider

\cvevent{M.Phys.\ in Physics}{University of Warwick}{Sept 2013 -- June 2017}{}
\small \textbf{Grade:} First Class Honours \\
\textbf{Supervisor:} Dr. Jeremy Sloan (Microscopy) \\
\textbf{Project:} \textit{Characterising low-dimensional `extreme nanowires' of phase change materials in single-walled carbon nanotubes}

\divider

\cvevent{A Levels \& GCSEs}{Wrenn Academy \& Sixth Form}{September 2010 -- June 2013}{}
\small \textbf{A2:} Maths (A*), History (A*), Physics (A), Chemistry (A) \\
\textbf{AS:} Above (AAAA), Further Maths (A), Philosophy (B) \\
\textbf{GCSE:} 9(A*) incl. Maths, Physics and English Language, 5(A) incl. Astronomy
